### 2025-03-21 writing/manuscript.tex
first look regression analysis

\begin{figure}[H]
  \centering
  \caption{Effect of the Bonus on Referrals}
  \begin{subfigure}[t]{0.7\textwidth}
    \centering
      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/reading_combined.png}
      \caption{Reading}  
      \label{fig:reading_combined}
  \end{subfigure}
  \begin{subfigure}[t]{0.7\textwidth}
    \centering
      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/math_combined.png}
      \caption{Math}
      \label{fig:math_combined}
  \end{subfigure}
  \label{fig:both_combined}
  \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions. We test differences in across conditions using two-sample $t$-tests and fin that all differences are statistically significant ($p < 0.001$). The bottom panel shows the average standardized math and tie strength of referrals across conditions. We test differences in across conditions using two-sample $t$-tests and fin that all differences are statistically significant ($p < 0.001$). For both math and reading, referred students }
\end{figure}

@@

  \begin{figure}[H]
    \centering
    \caption{Participant network performance by subject and SES}\label{performance}
    \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_peer_performance.png}
    \begin{tablenotes}
      \footnotesize
      \item[] \textit{Note:} This figure displays the network average math and reading z-scores across referrer SES. We test differences between math and reading scores within using paired $t$-tests. For both math and reading scores, differences between Low and Middle SES ($p < 0.001$), Low and High SES ($p < 0.001$), and Middle and High SES ($p = 0.001$) are all statistically significant.
    \end{tablenotes}
  \end{figure}

@@

  \begin{figure}[H]
    \centering
    \caption{Participant network composition by SES}
    \includegraphics[width=0.6\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_distribution.png}
    \label{fig:baseline_ses}
    \caption*{\footnotesize\textit{Note:} This figure displays the composition of networks by SES. We test differences in proportions of peer connections across SES groups using two-sample tests of proportions. All differences are statistically significant ($p <$ 0.001): Low SES students are more likely to connect with Low SES peers than Middle or High SES students; Middle SES students form more connections with Middle SES peers than Low SES students; and High SES students have the highest proportion of High SES connections. These patterns reveal strong homophily in network formation across all SES groups.
    }
\end{figure}

\begin{figure}[H]
  \centering
  \caption{Participant network composition by SES}
  \includegraphics[width=0.6\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/z_ses_tie_strength.png}
  \label{fig:tie_ses}
  \caption*{\footnotesize\textit{Note:} This figure displays the standardized tie strength by SES. We test differences in standardized tie strength across SES groups using two-sample $t$-tests. All differences are statistically significant ($p < 0.001$) except for the comparison between Middle and High SES students' connections to Low SES peers ($p = 0.65$). The standardized tie strength for High SES students with other High SES students is substantially positive (0.26), while all other tie strengths are negative or near zero. These patterns reveal strong homophily in network formation, particularly among High SES students, while Low SES students show moderate homophily patterns.}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \caption{Effect of the Bonus on Referrals}
  \begin{subfigure}[t]{0.7\textwidth}
    \centering
      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/reading_combined.png}
      \caption{Reading}  
      \label{fig:reading_combined}
  \end{subfigure}
  \begin{subfigure}[t]{0.7\textwidth}
    \centering
      \includegraphics[width=\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/math_combined.png}
      \caption{Math}
      \label{fig:math_combined}
  \end{subfigure}
  \label{fig:both_combined}
  \caption*{\footnotesize\textit{Note:} The top panel compares the reading scores and tie strength of referrals across conditions. The bottom panel shows the average standardized math and tie strength of referrals across conditions. We test differences in across conditions using two-sample $t$-tests and find no meaningful differences. For both math and reading, treatment causes no significant changes in referral performance or tie strength.}
\end{figure}

@@

  \begin{figure}[H]
    \centering
    \caption{Participant network performance by subject and SES}\label{performance}
    \includegraphics[width=0.6\linewidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_peer_performance.png}
    \begin{tablenotes}
      \footnotesize
      \item[] \textit{Note:} This figure displays the network average math and reading z-scores across referrer SES. We test differences between scores across SES using paired $t$-tests. For both math and reading scores, all differences between SES groups are statistically significant (all $p \leq 0.001$).
    \end{tablenotes}
  \end{figure}

@@

  \begin{figure}[H]
    \centering
    \caption{Participant network composition by SES}
    \includegraphics[width=0.6\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/ses_distribution.png}
    \label{fig:baseline_ses}
    \caption*{\footnotesize\textit{Note:} This figure displays the composition of networks by SES. We test differences in proportions of peer connections across SES groups using two-sample tests of proportions. All differences are statistically significant ($p <$ 0.001): Low SES students are more likely to connect with Low SES peers than Middle or High SES students; Middle SES students form more connections with Middle SES peers than Low SES students; and High SES students have the highest proportion of High SES connections.
    }
\end{figure}

\begin{figure}[H]
  \centering
  \caption{Participant network composition by SES}
  \includegraphics[width=0.6\textwidth]{/Users/reha.tuncer/Documents/GitHub/icfes-referrals/figures/z_ses_tie_strength.png}
  \label{fig:tie_ses}
  \caption*{\footnotesize\textit{Note:} This figure displays the standardized tie strength by SES. We test differences in standardized tie strength across SES groups using two-sample $t$-tests. All differences are statistically significant ($p < 0.001$) except for the comparison between Middle and High SES students' connections to Low SES peers ($p = 0.65$). The standardized tie strength for High SES students with other High SES students is substantially positive (0.26), while all other tie strengths are negative or near zero.}
\end{figure}
